\textbf{EECS 340: Assignment 1}

### 2020-01-28 assignment_1/article.tex
💄 Fix language after proofread.

\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
\date{Due on 01/27/2020, submitted on 01/26/2020 \\ EECS 340, Dr. Koyuturk}
\maketitle

@@

Now similarly, Let $e$ for $e \in \mathbb{Z^+}$ being the greatest common divisor of $x-y$ and $y$. We may therefore have $x - y = le$ and $y = me$ for $l, m \in \mathbb{Z^+}$. Then we may infer:
\begin{gather}
    x = (x - y) + y = le + me = e(l + m)
\end{gather}

@@

\section{Problem 2}
\subsection{(a)}

@@

% l = red, p = black
\begin{algorithm}
\caption{Kepler442b(m, n)}\label{Kepler442b}
\begin{algorithmic}[1]
\Procedure{}{}
\State $l \gets m$
\State $p \gets n$
\While {$(l + p) > 1$}
    \State \text{Let two individuals fight each other.}
    \If {\text{Both individuals are Lydians}}
        \State $l \gets l - 1$
    \ElsIf {\text{Both individuals are Pisidians}}
        \State $p \gets p - 2$
        \State $l \gets l + 1$
    \Else
        \State $l \gets l - 1$
    \EndIf
\EndWhile
\State \Return $l, p$
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

When the \inlinecode{while} loop terminates at $l + p = 1$ there can only be two cases:
\begin{gather}
    l = 1, \ p = 0 \ \ (n \bmod 2 = 0) \\
    l = 0, \ p = 1 \ \ (n \bmod 2 = 1)
\end{gather}

@@

As the above two \textit{Equations} satisfy the assumption of the loop invariant, we may say that the scenario of $k = 1$ is true.

>>>>

\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Zhitao (Robert) CHEN, \inlinecode{zxc325}}
\date{Due and submitted on 01/27/2020 \\ EECS 340, Dr. Koyuturk}
\maketitle

@@

Now similarly, let $e$ for $e \in \mathbb{Z^+}$ being the greatest common divisor of $x-y$ and $y$. We may therefore have $x - y = le$ and $y = me$ for $l, m \in \mathbb{Z^+}$. Then we may infer:
\begin{gather}
    x = (x - y) + y = le + me = e(l + m)
\end{gather}

@@

\section{Problem 2}
As suggested by Dr. Koyuturk, this is a kindly reminder to the grader that this problem is answered with the assumption of the first index of an array being $[0]$. If you'd prefer $[1]$, please let us know through Canvas comment section and we will adjust accordingly in our future submission.
\subsection{(a)}

@@

% l = red, p = black
\begin{algorithm}
\caption{Kepler442bArena(m, n)}\label{Kepler442b}
\begin{algorithmic}[1]
\Procedure{}{}
\State $l \gets m$
\State $p \gets n$
\While {$(l + p) > 1$}
    \State \text{Let two individuals fight each other.}
    \If {\text{Both individuals are Lydians}}
        \State $l \gets l - 1$
    \ElsIf {\text{Both individuals are Pisidians}}
        \State $p \gets p - 2$
        \State $l \gets l + 1$
    \Else
        \State $l \gets l - 1$
    \EndIf
\EndWhile
\State \Return $l, p$
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

When the \inlinecode{while} loop terminates at $l + p = 1$, there can only be two cases:
\begin{gather}
    l = 1, \ p = 0 \ \ (n \bmod 2 = 0) \\
    l = 0, \ p = 1 \ \ (n \bmod 2 = 1)
\end{gather}

@@

As the above two \textit{Equations} satisfy the assumption of the loop invariant, we may say that the scenario of $k = 1$ is held true.
